### 2017-01-27 main.tex
Clean up don't-use-citation-as-sentence-subject changes.

If precise moments in song can reliably be detected quickly enough to
trigger other apparatus during singing, then this consistency of
behaviour allows a variety of experiments.  A common area of study
with this song-triggering technique is the anterior forebrain pathway
(AFP), a homologue of mammalian basal ganglia consisting of a few
distinct brain areas concerned with the learning and production of
song.  For example, stimulation of the lateral magnocellular nucleus
of the anterior nidopallium (LMAN)---the output nucleus of the
AFP---at precisely timed moments during song shows that this area
controls specific variables in song output \cite{Kao2005}.
Song-synchronised stimulation of LMAN and the high vocal centre (HVC)
in one hemisphere or the other showed that control of song rapidly
switches between hemispheres \cite{Wang2008interhemispheric}.
Feedback experiments have shown that Field L and the caudolateral
mesopallium may hold a representation of song against which auditory
signals are compared \cite{Keller2009}.  Renditions of a syllable that
were disrupted by white noise when they were slightly above (or below)
the syllable's average pitch showed that the apparently random natural
variability in songbird motor output is used to drive change in the
song \cite{Tumer2007pitchshift}. Furthermore, AFP produces a
corrective signal to bias song away from those disruptions
\cite{Andalman2009}. The
song change is isolated to within roughly 10 milliseconds (ms) of the
stimulus, and the shape of the learned response can be predicted by
a simple mechanism \cite{Charlesworth2011learning}.

AFP transfers the error signal to
the robust nucleus of the arcopallium (RA) using
NMDA-receptor--mediated glutamatergic transmission \cite{Warren2011}. By looking at song
recovery after applying the same pitch-shift paradigm,
the caudal medial nidopallium is
implicated in memorising or recalling a recent song target, but for
neither auditory processing nor directed motor learning \cite{Canopoli2014}.

@@

A variety of syllable-triggering systems have been used, but few have
been documented or characterised in detail.  In 1999,
detection was achieved by a group of IIR filters with hand-tuned logical
operators \cite{Leonardo1999}.  The system had a latency of 50 or 100 ms,
and no reported data on jitter or accuracy.  As access to
computational resources has improved, approaches have changed: in
2009, detection still used hand-tuned filters, but implemented
on a Tucker-Davis Technologies digital signal processor \cite{Andalman2009}.  This
achieved a latency of around 4 ms, but as with other filter-bank techniques, it
is not strictly a syllable detector but rather a pitch and timbre
detector---it cannot identify a frequency sweep, or distinguish a
short chirp from a long one---and thus requires careful selection of
target syllables.  Furthermore, the method is neither inexpensive nor,
based on our experience with a similar technique, accurate.
Also in 2009, another group applied a neural network to a spectral image of
song \cite{Keller2009}.  They reported a jitter of 4.3 ms, but further implementation and
performance details are not available.  In 2011, a detector was implemented by
matching spectral templates to stable portions of syllables in 8 ms
segments \cite{Warren2011}.  This detector achieved a jitter of 4.5 ms, and false-negative and
false-positive rates of up to 2\% and 4\% respectively.  Hardware
requirements and ease of use were not reported.  In 2013,
a group described in detail a system that matches spectral
images of template syllables using a correlation coefficient \cite{Skocik2013}.  With a
fast desktop (Intel i7 six-core) running Linux and equipped with a
National Instruments data acquisition card, it boasts a hardware-only
(not accounting for the time taken to compute a match with a syllable)
latency and jitter of just a few microseconds, and the detection
computation they use should not much increase that.  They reported
false-negative rates around 4\% and 7\% for zebra finches and
Bengalese finches respectively, measured on a small dataset.  In much
other work, an allusion is made to a syllable detector, but no further
information is provided.

>>>>

If precise moments in song can reliably be detected quickly enough to
trigger other apparatus during singing, then this consistency of
behaviour allows a variety of experiments.  A common area of study
with song-triggered experiments is the anterior forebrain pathway
(AFP), a homologue of mammalian basal ganglia consisting of a few
distinct brain areas concerned with the learning and production of
song.  For example, stimulation of the lateral magnocellular nucleus
of the anterior nidopallium (LMAN)---the output nucleus of the
AFP---at precisely timed moments during song showed that this area
controls specific variables in song output \cite{Kao2005}.
Song-synchronised stimulation of LMAN and the high vocal centre (HVC)
in one hemisphere or the other showed that control of song rapidly
switches between hemispheres \cite{Wang2008interhemispheric}.
Feedback experiments have shown that Field L and the caudolateral
mesopallium may hold a representation of song against which auditory
signals are compared \cite{Keller2009}.  Renditions of a syllable that
were disrupted by white noise when they were slightly above (or below)
the syllable's average pitch showed that the apparently random natural
variability in songbird motor output is used to drive change in the
song \cite{Tumer2007pitchshift}. Furthermore, AFP produces a
corrective signal to bias song away from those disruptions
\cite{Andalman2009}. The song change is isolated to within roughly 10
milliseconds (ms) of the stimulus, and the shape of the learned
response can be predicted by a simple mechanism
\cite{Charlesworth2011learning}. AFP transfers the error signal to the
robust nucleus of the arcopallium (RA) using NMDA-receptor--mediated
glutamatergic transmission \cite{Warren2011}. The course of song
recovery after applying such a pitch-shift paradigm showed that the
caudal medial nidopallium is implicated in memorising or recalling a
recent song target, but in neither auditory processing nor directed
motor learning \cite{Canopoli2014}.

@@

A variety of syllable-triggering systems have been used, but few have
been documented or characterised in detail.  In 1999,
detection was achieved by a group of IIR filters with hand-tuned logical
operators \cite{Leonardo1999}.  The system had a latency of 50 or 100 ms,
and jitter or accuracy were not reported.  As access to
computational resources has improved, approaches have changed: in
2009, hand-tuned filters were implemented on a Tucker-Davis Technologies digital signal processor, bringing latency down to around 4 ms \cite{Andalman2009}. But as with other filter-bank techniques, it
is not strictly a syllable detector but rather a pitch and timbre
detector---it cannot identify a frequency sweep, or distinguish a
short chirp from a long one---and thus requires careful selection of
target syllables.  Furthermore, the method is neither inexpensive nor,
based on our experience with a similar technique, accurate.
2009 also saw the application of a neural network to a spectral image of
song \cite{Keller2009}.  They reported a jitter of 4.3 ms, but further implementation and
performance details are not available.  In 2011, stable portions of syllables were matched to spectral templates in 8-ms
segments \cite{Warren2011}.  This detector achieved a jitter of 4.5 ms, and false-negative and
false-positive rates of up to 2\% and 4\% respectively.  Hardware
requirements and ease of use were not reported.  In 2013, spectral
images of template syllables were compared to song using a correlation coefficient \cite{Skocik2013}.  With a
fast desktop (Intel i7 six-core) running Linux and equipped with a
National Instruments data acquisition card, it boasts a hardware-only
(not accounting for the time taken to compute a match with a syllable)
latency and jitter of just a few microseconds, and the detection
computation they use should not much increase that.  They reported
false-negative rates around 4\% and 7\% for zebra finches and
Bengalese finches respectively, measured on a small dataset.  In much
other work, a syllable detector is alluded to, but not described.
